---
title: "Getting Started with Modeltime GluonTS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with Modeltime GluonTS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE,
  fig.align = "center",
  out.width = "90%",
  fig.width = 7,
  fig.height = 5
)
```

## Making an DeepAR Model

Let's get started by making a __DeepAR Model.__ In a matter of minutes, you'll generate the 7 forecasts shown below. If you'd like to improve your time series forecasting abilities, then please take my [High-Performance Time Series Course](https://university.business-science.io/p/ds4b-203-r-high-performance-time-series-forecasting/). 

```{r, echo=F}
library(tidyverse)
library(modeltime)
library(modeltime.gluonts)

modeltime_forecast_tbl <- read_rds("modeltime_forecast_tbl.rds")

modeltime_forecast_tbl %>%
  plot_modeltime_forecast(
    .facet_ncol   = 3, 
    .facet_scales = "free",
    .interactive  = FALSE
  )
```


## Libraries

Load the following libraries. 

```{r setup}
library(modeltime.gluonts)
library(tidymodels)
library(tidyverse)
library(timetk)
```

## Installation

Next, set up the Python Environment with `install_gluonts()`. You only need to run this one time, and then you are good to go. 

```{r, eval=F}
install_gluonts()
```

We have a more detailed installation instructions and troubleshooting guidance in our [Installation Guide](https://business-science.github.io/modeltime.gluonts/articles/managing-envs.html). 

## Time Series Data

We'll use the `walmart_sales_weekly` dataset, which contains 7 weekly time series of sales data for various departments in a Walmart Store.

```{r}
data <- walmart_sales_weekly %>%
  select(id, Date, Weekly_Sales) %>%
  set_names(c("id", "date", "value"))

data %>%
  group_by(id) %>%
  plot_time_series(
    date, 
    value, 
    .facet_ncol = 3, 
    .interactive = FALSE
  )
```

We'll create the forecast region using `future_frame()`. We are forecasting 1 week (24x7 timestamps) into the future.

```{r}
HORIZON <- 52

new_data <- data %>%
  group_by(id) %>%
  future_frame(.length_out = HORIZON) %>%
  ungroup()

new_data
```


## Making a DeepAR Model

We'll create a DeepAR model using the `deep_ar()` function. 

- This is a univariate modeling algorithm that uses Deep Learning and Autoregression. 
- We select the GluonTS version by setting the engine to `gluonts_deepar`.



```{r, eval = FALSE}
model_fit_deepar <- deep_ar(
  id                    = "id",
  freq                  = "W",
  prediction_length     = HORIZON,
  lookback_length       = 2*HORIZON,
  epochs                = 5
) %>%
  set_engine("gluonts_deepar") %>%
  fit(value ~ date + id, data)
```


## Forecasting 

With a model in hand, we can simply follow the [Modeltime Workflow](https://business-science.github.io/modeltime/) to generate a forecast for the multiple time series groups. 

```{r, eval=F}
modeltime_forecast_tbl <- modeltime_table(
  model_fit_deepar
) %>%
  modeltime_forecast(
    new_data    = new_data,
    actual_data = data,
    keep_data   = TRUE
  ) %>%
  group_by(id) 
```

We can visualize the forecast with `plot_modeltime_forecast()`.

```{r}
modeltime_forecast_tbl %>%
  plot_modeltime_forecast(
    .conf_interval_show = FALSE, 
    .facet_ncol         = 3, 
    .facet_scales       = "free",
    .interactive        = FALSE
  )
```


## Saving and Loading Models

GluonTS models will need to "serialized" (a fancy word for saved to a directory that contains the recipe for recreating the models). To save the models, use `save_gluonts_model()`.

- Provide a directory where you want to save the model. 
- This saves all of the model files in the directory.

```{r, eval = FALSE}
model_fit_deepar %>%
  save_gluonts_model(path = "deepar_model", overwrite = TRUE)
```


You can reload the model into R using `load_gluonts_model()`.

```{r, eval=FALSE}
model_fit_deepar <- load_gluonts_model("deepar_model")
```




## Take the High-Performance Forecasting Course

> Become the forecasting expert for your organization

<a href="https://university.business-science.io/p/ds4b-203-r-high-performance-time-series-forecasting/" target="_blank"><img src="https://www.filepicker.io/api/file/bKyqVAi5Qi64sS05QYLk" alt="High-Performance Time Series Forecasting Course" width="100%" style="box-shadow: 0 0 5px 2px rgba(0, 0, 0, .5);"/></a>

[_High-Performance Time Series Course_](https://university.business-science.io/p/ds4b-203-r-high-performance-time-series-forecasting/)

### Time Series is Changing

Time series is changing. __Businesses now need 10,000+ time series forecasts every day.__ This is what I call a _High-Performance Time Series Forecasting System (HPTSF)_ - Accurate, Robust, and Scalable Forecasting. 

 __High-Performance Forecasting Systems will save companies by improving accuracy and scalability.__ Imagine what will happen to your career if you can provide your organization a "High-Performance Time Series Forecasting System" (HPTSF System).

### How to Learn High-Performance Time Series Forecasting

I teach how to build a HPTFS System in my [__High-Performance Time Series Forecasting Course__](https://university.business-science.io/p/ds4b-203-r-high-performance-time-series-forecasting). You will learn:

- __Time Series Machine Learning__ (cutting-edge) with `Modeltime` - 30+ Models (Prophet, ARIMA, XGBoost, Random Forest, & many more)
- __Deep Learning__ with `GluonTS` (Competition Winners)
- __Time Series Preprocessing__, Noise Reduction, & Anomaly Detection
- __Feature engineering__ using lagged variables & external regressors
- __Hyperparameter Tuning__
- __Time series cross-validation__
- __Ensembling__ Multiple Machine Learning & Univariate Modeling Techniques (Competition Winner)
- __Scalable Forecasting__ - Forecast 1000+ time series in parallel
- and more.

<p class="text-center" style="font-size:24px;">
Become the Time Series Expert for your organization.
</p>
<br>
<p class="text-center" style="font-size:30px;">
<a href="https://university.business-science.io/p/ds4b-203-r-high-performance-time-series-forecasting">Take the High-Performance Time Series Forecasting Course</a>
</p>


